oolong: An R package for validating  automated content analysis tools

### 2020-10-15 paper/paper.rmd
Fixing recommendation about which version to install, ref #31
Making printing oolong summary smarter, ref #31
Update paper to explain the diagnostic plot, ref #31

---
title: 'oolong: An R package for validating  automated content analysis tools'
tags:
  - R
  - text analysis
  - topic model
  - sentiment analysis
  - validation
authors:
  - name: Chung-hong Chan
    orcid: 0000-0003-0872-7098
    affiliation: 1
  - name: Marius Sältzer
    orcid: 0000-0002-8604-4666
    affiliation: 1
affiliations:
 - name: Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim
   index: 1
citation_author: Chan & Sältzer.
date: 3 July 2020
year: 2020
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---

@@

```{r}
abstracts
```

@@

```{r}
tibble(text = trump2k)
```

@@

Additional diagnostic plots can also be displayed.

@@

The 4 subplots from left to right, top to bottom are: 1) correlation between human judgement and target value; 2) Bland-Altman plot; 3) correlation between target value and content length and 4) Cook's distance of all data point. These plots are helpful to determine criterion validity, agreement, robustness against content length and outliers of the target value.

>>>>

---
title: 'oolong: An R package for validating  automated content analysis tools'
tags:
  - R
  - text analysis
  - topic model
  - sentiment analysis
  - validation
authors:
  - name: Chung-hong Chan
    orcid: 0000-0003-0872-7098
    affiliation: 1
  - name: Marius Sältzer
    orcid: 0000-0002-8604-4666
    affiliation: 1
affiliations:
 - name: Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim
   index: 1
citation_author: Chan & Sältzer.
date: 15 October 2020
year: 2020
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---

@@

@@

@@

Additional diagnostic plots can also be displayed (Figure 2).

@@

The 4 subplots from left to right, top to bottom are:

1. Correlation between human judgement and target value - A strong correlation between the two is an indicator of criterion validity of the target value.
2. Bland-Altman plot - If the dots are randomly scattering around the mean value (solid line), it is an indicator of good agreement between human judgement and the target value.
3. Correlation between target value and content length - If there is no strong correlation between the target value and content length, it is an indicator of robustness against the influence of content length [see @chan_4b].
4. Cook's distance of all data points - if there are only a few dots above the threshold (dotted line), it is an indicator of robustness against the influence of outliers.
